---
title: "Lab 6"
author: "Kiera Matiska"
date: "11/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Attach Packages
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Rank-based text example

Mann-Whitney U (non-parametric alternative to an unpaired 2-sample t-test)

H0: Equal ranks (or medians)
HA: Ranks are not equal (or medians are not equal)

### Create samples

`set.seed()` to create "pseudorandom, but reproducible samples"

```{r}
# Random sample from a sequence
set.seed(1414)
# sample.int creates a random sample
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

Take a quick look at the distributions using `hist()`.

```{r}
hist(gp_1)
hist(gp_2)
# More likely to come from a uniform data

# Unknown for both because there is not enough samples and data
```

Try a t-test so we can compare the results:

```{r}
ttest <- t.test(gp_1, gp_2)

# If these data were paired, I can just add the argument 'paired' = "TRUE"' within the t.test() function

# p-value means: If the two samples come from populations with the same mean, then there is a 19.8% chance of finding sample means from the same population that are at least this far apart.
```

This p-value means that IF our samples are dwarn from populations with the same mean (i.e., if the null hypothesis is true), there is `r round(ttest$p.value,2)` probably of finding sample means *at least as different* as mine by random chance.

[A more comprehensive explanation of difference between groups... actually means, data spread, effect size]... there is no significant difference (t(df) = t-statistic value, p = ).

df = measure of pooled sample sizes

### Mann-Whitney U rank-based test

We use the `wilcox.test()` function to perform a two-sample rank-based test.

```{r}
mwu <- wilcox.test(gp_1, gp_2)
```

This p-value means that IF our samples are drawn from populations with the same ranks, there is a 28% chance of finding sample medians at least as different as ours by random chance.

No significant difference in medians (Mann-Whitney U; U = `r mwu$statistic`, p = `r round(mwu$p.value, 2)`).

The medians of group A (M = 22.4 g) and group B (M = 31.2 g) did not differ significantly (Mann-Whitney U, ...).

## Simple linear regression

Two *continuous quantitative* variables that you are trying to understand the relationship between, and you think that a linear relationship makes sense.

Use the `penguins` data from {palmerpenguins}, exploring flipper length (x) versus body mass (y)

```{r}
# Use view(penguins to look at it
# Make an exploratory scatterplot of penguin flipper length (x-axis) versus body mass (y-axis)

ggplot(data = penguins,
       aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point() +
  geom_smooth(method = "lm") # Adds a linear regression; y = mx + b

# Does this look like it could be a linear relationship? Does it make sense?
```

### Find the model estimates (coefficients)

Use the `lm()` function for linear model

body_mass_g ~ <<<< tilde (not a minus sign)

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)

# body mass (g) = 49.69(flipper length (mm)) - 5780.83
# [g] = [g / mm] * [mm] - [g]
# Does the intercept have meaning: That is the expected mass for a penguin that has 0 mm of flipper; it doesn't make sense because nothing on this planet is without mass.
```

Model Coefficients: `r penguin_lm$coefficients`
Flipper length coefficient: `r penguin_lm$coefficients[2]`

### Use `broom::tidy()` to get a tidy output from lm()

```{r}
penguin_lm_tidy <- tidy(penguin_lm)

penguin_lm_tidy
```

### Use broom::glance() to get output of model fit and statistical significance

```{r}
penguin_lm_glance <- glance(penguin_lm)

penguin_lm_glance
```

### Use equatiomatic::extract_eq() to return the model in LaTeX

```{r}
extract_eq(model = penguin_lm, use_coefs = TRUE)
```

### Use plot() funtion to automatically produce diagnotic plots

```{r}
plot(penguin_lm)
```

